Newton-Type Methods for Non-Convex Optimization Under Inexact Hessian Information

### 2017-11-05 Paper-Presentation/main.tex
Started Finite-sum minimization

\begin{frame}{Characteristics of Inexact Hessian in these methods}
\begin{itemize}
\item<1->{Same convergence rates with actual Hessians}
\item<2->{Both the methods - trust region and cubic regularization, at termination satisfy
  \begin{equation*}
  ||\g F(\xbold_{T})|| \leq \epsilon_{g} \hspace{4mm} \text{ and } \hspace{4mm} \mineig(\h F(\xbold_{T})) \geq -(\epsilon_{h} + \epsilon)
  \end{equation*}
  \uncover<3->{in terms of the optimal point definition, these are \((\epsilon_{g}, \epsilon_{h} + \epsilon)\)-optimal points}
} 
\end{itemize}
\end{frame}
\end{document}

>>>>

\begin{frame}{Characteristics of Inexact Hessian in these methods}
\begin{itemize}
\item<1->{Same convergence rates with actual Hessians}
\item<2->{Both the methods - trust region and cubic regularization, at termination satisfy
  \begin{equation*}
  ||\g F(\xbold_{T})|| \leq \epsilon_{g} \hspace{4mm} \text{ and } \hspace{4mm} \mineig(\h F(\xbold_{T})) \geq -(\epsilon_{h} + \epsilon)
  \end{equation*}
  \uncover<3->{in terms of the optimal point definition, these are \((\epsilon_{g}, \epsilon_{h} + \epsilon)\)-optimal points}
} 
\end{itemize}
\end{frame}

\section{Finite-Sum Minimization}
\begin{frame}{Randomized Sub-sampling}
\begin{itemize}
\item<1->{Consider a modified unconstrained optimization problem
  \begin{equation}
    \min_{\xbold \in \mathbb{R}^{d}} F(\xbold) \triangleq \frac{1}{n}\displaystyle \sum_{i=1}^{n} f_{i}(\xbold)
  \end{equation}
where each \(f_{i}\) is smooth, but possibly non-convex.}
\item<2->{Seen in Machine Learning problems, where each \(f_{i}\) corresponds to the loss or mis-fit due to the \(i^{th}\) sample in the mini-batch/batch}
\item<3->{Large-scale problems have \(n, d >> 1\).}
\item<4->{Consider a probability distribution over \({1, 2, \ldots, n}\), denoted by \(\mathbf{p} = \{p_{i}\}_{i=1}^{n}\) and \(Pr(X = i) = p_{i} > 0, \hspace{2mm} \sum p_{i} = 1\). Based on \(\mathbf{p}\), we pick a sample \(\mathcal{S}\).}
\item<5->{Define the sub-sampled Hessian to be:
  \begin{equation}
    H(\xbold) \triangleq \frac{1}{n|\mathcal{S}|}\sum_{j \in \mathcal{S}} \frac{1}{p_{j}} \h f_{j}(\xbold)
  \end{equation}
}
\end{itemize}
\end{frame}

\begin{frame}{Randomized Sub-Sampling}
\begin{theorem}
Consider \(\displaystyle \sup_{\xbold\in\mathbb{R}^{d}} ||\h f_{i}(\xbold)|| \leq K_{i}, \hspace{2mm} \forall i \in \{1, 2, \ldots, n\}\). Let \(\displaystyle K_{\max} = \max_{i=1,\ldots, n} K_{i}\) and \(\hat{K} = \frac{1}{n} \displaystyle \sum_{i=1}^{n} K_{i}\). If \(p_{i} = \frac{1}{n} \hspace{1mm} \forall i \in \{1, 2, \ldots, n\}\), and \(|\mathcal{S}| \geq \frac{16K^{2}_{max}}{\epsilon^{2}}\log\frac{2d}{\delta} \), then with probability at least \(1 - \delta\), we have:
\begin{equation}
Pr\left(||H(\xbold) - \h F(\xbold)|| \leq \epsilon\right) \geq 1 - \delta
\end{equation}
\end{theorem}
\pause
\uncover<2->{Two major implications:}
\begin{itemize}
\item<3->{Higher the value of \(d\), more larger sample set is required. But this dependence is logarithmic.}
\item<4->{Higher the number of samples, lower the value of \(\epsilon\), in turn better ``inexact'' Hessian.}
\end{itemize}
\end{frame}
\end{document}
